My title

### 2024-03-11 paper/paper.qmd
update.

toronto_shelters_data_first_model_rstanarm <-
  tibble(
    sigma = rep(rexp(n = draws, rate = 1), times = 16),
    beta_0 = rep(rnorm(n = draws, mean = 0, sd = 2.5), times = 16),
    beta_1 = rep(rnorm(n = draws, mean = 8, sd = 2.5), times = 16),
    five_km_time = rep(15:30, each = draws),
    occupancy_rate_rooms = occupancy_rate_rooms, 
    mu = beta_0 + beta_1 * occupancy_rate_rooms
  ) |>
  rowwise() |>
  mutate(
    capacity_actual_room = rnorm(n = 1, mean = mu, sd = sigma)
  )

toronto_shelters_data_first_model_rstanarm |>
  ggplot(aes(x = occupancy_rate_rooms, y = capacity_actual_room)) +
  geom_point(alpha = 0.1) +
  theme_classic()
```

@@

modelsummary::modelsummary(
  list(
    "usage model" = toronto_shelters_data_first_model_rstanarm
  ),
  statistic = "mad",
  fmt = 2
)
```

>>>>

occupancy_rate_rooms <- runif(n = draws * 16, min = 0.5, max = 1.5)

toronto_shelters_clean <-
  tibble(
    sigma = rep(rexp(n = draws, rate = 1), times = 16),
    beta_0 = rep(rnorm(n = draws, mean = 0, sd = 2.5), times = 16),
    beta_1 = rep(rnorm(n = draws, mean = 8, sd = 2.5), times = 16),
    five_km_time = rep(15:30, each = draws),
    occupancy_rate_rooms = occupancy_rate_rooms, 
    mu = beta_0 + beta_1 * occupancy_rate_rooms
  ) |>
  rowwise() |>
  mutate(
    capacity_actual_room = rnorm(n = 1, mean = mu, sd = sigma)
  )

toronto_shelters_clean |>
  ggplot(aes(x = occupancy_rate_rooms, y = capacity_actual_room)) +
  geom_point(alpha = 0.1) +
  theme_classic()
```

@@

modelsummary(toronto_shelters_data_first_model_rstanarm)
```
